
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## For shelduck
Load data as escape distance for the two used UAV models


```{r}

directory <- "F:/Vadehavet/Frames_geo"

Gravand <- file.path(directory,"/Responsafstand_gravand.csv")
Gravand
Gravand <- read.csv(file=Gravand, header= TRUE)
str(Gravand)

Gravand <- Gravand[order(Gravand$height,decreasing = TRUE),]
Gravand

#Subset efter drone model både flyvninger og nr_bird
Gravand_nr <- Gravand[order(Gravand$nr_birds,decreasing = TRUE),]
Gravand_nr

# For Phantom
Grav_phan <- Gravand[Gravand$id == "Phantom", ]
Grav_phan_nr <- Gravand_nr[Gravand_nr$id == "Phantom", ]
Grav_phan
Grav_phan_nr

# For Mavic
Grav_mavic <- Gravand[Gravand$id == "Mavic", ]
Grav_mavic_nr <- Gravand_nr[Gravand_nr$id == "Mavic", ]
Grav_mavic
Grav_mavic_nr

```

First we find the number of unique flyover heigths with unique(),
then we find the percentage of flights which are at that flyover height and 

```{r}
Grav_phan_uni.vec <- unique(Grav_phan$height)
Grav_phan_perc_vec <- rep('NA',length(Grav_phan_uni.vec))
Grav_phan_perc_vec
for (i in 1:length(unique(Grav_phan$height))){
   Grav_phan_perc_vec[i] <- sum((Grav_phan$height==Grav_phan_uni.vec[i])/length(Grav_phan$height))
}
Grav_phan_cum_vec <- cumsum(Grav_phan_perc_vec)
Grav_phan_cum_vec
```

# For Mavic

First we find the number of unique flyover heigths with unique(),
then we find the percentage of flights which are at that flyover height and 

```{r}
Grav_mavic_uni.vec <- unique(Grav_mavic$height)
Grav_mavic_perc_vec <- rep('NA',length(Grav_mavic_uni.vec))
Grav_mavic_perc_vec
for (i in 1:length(unique(Grav_mavic$height))){
   Grav_mavic_perc_vec[i] <- sum((Grav_mavic$height==Grav_mavic_uni.vec[i])/length(Grav_mavic$height))
}
Grav_mavic_cum_vec <- cumsum(Grav_mavic_perc_vec)
Grav_mavic_cum_vec
```

Lav dataframes

```{r}
phan_grav <- data.frame(Grav_phan_uni.vec,Grav_phan_cum_vec,id="Phantom")
names(phan_grav) <- c("hoejde","percent","id")
ingen_forstyr <- cbind.data.frame(c(100),0,"Phantom")

names(ingen_forstyr) <- c("hoejde","percent","id")

phan_grav <- rbind.data.frame(ingen_forstyr,phan_grav)
phan_grav


mavic_grav <- data.frame(Grav_mavic_uni.vec,Grav_mavic_cum_vec,id="Mavic")
names(mavic_grav) <- c("hoejde","percent","id")
ingen_forstyr <- cbind.data.frame(c(100),0,"Mavic")
names(ingen_forstyr) <- c("hoejde","percent","id")

mavic_grav <- rbind.data.frame(ingen_forstyr,mavic_grav)
mavic_grav

# combine dataframes

Gravand_dat <- rbind.data.frame(phan_grav,mavic_grav)
Gravand_dat

```

Lav dataframes for nr fugle

```{r}
Grav_phan_nr

# combine dataframes

Gravand_nr_dat <- rbind.data.frame(Grav_phan_nr,Grav_mavic_nr)
Gravand_nr_dat

```


We then use ggplot to visualize each drone by itself

```{r}
p <- ggplot(data = Gravand_dat, aes(x = percent, y = hoejde, group = id,
                               color = id))
p + geom_point() +
  geom_smooth(method = "loess", se = FALSE,  fullrange = TRUE, span = 0.3) + ylim(0, 100) + xlim(0,1.01) +
  ggtitle("Escape distance Shelduck") + theme(plot.title = element_text(hjust = 0.5)) + 
  xlab("Percent disturbed") + ylab("Flying altitude")


```

We then use ggplot to visualize each drone by itself (nr fugle)

```{r}
p <- ggplot(data = Gravand_nr_dat, aes(x = nr_birds, y = height, group = id,
                               color = id))
p + geom_point() +
  geom_smooth(method = "gam", se = FALSE,  fullrange = TRUE, span = 0.5) + xlim(0,1000) + ylim(0, 100) +
  ggtitle("Escape distance Shelduck") + theme(plot.title = element_text(hjust = 0.5)) + 
  xlab("Flock size disturbed") + ylab("Flying altitude")


```

