
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## For Islandsk
Load data as escape distance for the two used UAV models


```{r}

directory <- "F:/Vadehavet/Frames_geo"

Islandsk <- file.path(directory,"/Responsafstand_Islandsk.csv")
Islandsk
Islandsk <- read.csv(file=Islandsk, header= TRUE)
str(Islandsk)

Islandsk <- Islandsk[order(Islandsk$height,decreasing = TRUE),]
Islandsk


#Subset efter drone model
Islandsk_nr <- Islandsk[order(Islandsk$nr_birds,decreasing = TRUE),]
Islandsk_nr

# For Phantom
Islandsk_phan <- Islandsk[Islandsk$id == "Phantom", ]
Islandsk_phan

# For Mavic
Islandsk_mavic <- Islandsk[Islandsk$id == "Mavic", ]
Islandsk_mavic

#Subset efter drone model både flyvninger og nr_bird
# For Phantom
Islandsk_phan <- Islandsk[Islandsk$id == "Phantom", ]
Islandsk_phan_nr <- Islandsk_nr[Islandsk_nr$id == "Phantom", ]
Islandsk_phan
Islandsk_phan_nr

# For Mavic
Islandsk_mavic <- Islandsk[Islandsk$id == "Mavic", ]
Islandsk_mavic_nr <- Islandsk_nr[Islandsk_nr$id == "Mavic", ]
Islandsk_mavic
Islandsk_mavic_nr

```

First we find the number of unique flyover heigths with unique(),
then we find the percentage of flights which are at that flyover height and 

```{r}
Islandsk_phan_uni.vec <- unique(Islandsk_phan$height)
Islandsk_phan_perc_vec <- rep('NA',length(Islandsk_phan_uni.vec))
Islandsk_phan_perc_vec
for (i in 1:length(unique(Islandsk_phan$height))){
   Islandsk_phan_perc_vec[i] <- sum((Islandsk_phan$height==Islandsk_phan_uni.vec[i])/length(Islandsk_phan$height))
}
Islandsk_phan_cum_vec <- cumsum(Islandsk_phan_perc_vec)
Islandsk_phan_cum_vec
```

# For Mavic

First we find the number of unique flyover heigths with unique(),
then we find the percentage of flights which are at that flyover height and 

```{r}
Islandsk_mavic_uni.vec <- unique(Islandsk_mavic$height)
Islandsk_mavic_perc_vec <- rep('NA',length(Islandsk_mavic_uni.vec))
Islandsk_mavic_perc_vec
for (i in 1:length(unique(Islandsk_mavic$height))){
   Islandsk_mavic_perc_vec[i] <- sum((Islandsk_mavic$height==Islandsk_mavic_uni.vec[i])/length(Islandsk_mavic$height))
}
Islandsk_mavic_cum_vec <- cumsum(Islandsk_mavic_perc_vec)
Islandsk_mavic_cum_vec
```

Lav dataframes

```{r}
phan_Islandsk <- data.frame(Islandsk_phan_uni.vec,Islandsk_phan_cum_vec,id="Phantom")
names(phan_Islandsk) <- c("hoejde","percent","id")
ingen_forstyr <- cbind.data.frame(c(100),0,"Phantom")

names(ingen_forstyr) <- c("hoejde","percent","id")

phan_Islandsk <- rbind.data.frame(ingen_forstyr,phan_Islandsk)
phan_Islandsk


mavic_Islandsk <- data.frame(Islandsk_mavic_uni.vec,Islandsk_mavic_cum_vec,id="Mavic")
names(mavic_Islandsk) <- c("hoejde","percent","id")
ingen_forstyr <- cbind.data.frame(c(100),0,"Mavic")
names(ingen_forstyr) <- c("hoejde","percent","id")

mavic_Islandsk <- rbind.data.frame(ingen_forstyr,mavic_Islandsk)
mavic_Islandsk

# combine dataframes

Islandsk_dat <- rbind.data.frame(mavic_Islandsk)
Islandsk_dat

```

Lav dataframes for nr fugle

```{r}
Islandsk_phan_nr

# combine dataframes

Islandsk_nr_dat <- rbind.data.frame(Islandsk_mavic_nr)
Islandsk_nr_dat

```


We then use ggplot to visualize each drone by itself

```{r}
p <- ggplot(data = Islandsk_dat, aes(x = percent, y = hoejde, group = id,
                               color = id))
p + geom_point() +
  geom_smooth(method = "loess", se = FALSE,  fullrange = TRUE, span = 0.7) + scale_fill_manual(values=c("deepskyblue1","firebrick1"),aesthetics = "colour") + ylim(0, 100) + xlim(0,1.01) +
  ggtitle("Escape distance Golden plover") + theme(plot.title = element_text(hjust = 0.5)) + 
  xlab("Percent disturbed") + ylab("Flying altitude")


```

We then use ggplot to visualize each drone by itself (nr fugle)

```{r}
p <- ggplot(data = Islandsk_nr_dat, aes(x = nr_birds, y = height, group = id,
                              color = id))
p + geom_point() +
  geom_smooth(method = "gam", se = FALSE,  fullrange = TRUE, span = 0.5) + scale_fill_manual(values=c("deepskyblue1","firebrick1"),aesthetics = "colour") + xlim(0,1000) + ylim(0, 100) +
  ggtitle("Escape distance Golden plover") + theme(plot.title = element_text(hjust = 0.5)) + 
  xlab("Flock size disturbed") + ylab("Flying altitude")


```

