
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## For KLyde
Load data as escape distance for the two used UAV models


```{r}

directory <- "F:/Vadehavet/Frames_geo"

Klyde <- file.path(directory,"/Responsafstand_Klyde.csv")
Klyde
Klyde <- read.csv(file=Klyde, header= TRUE)
str(Klyde)

Klyde <- Klyde[order(Klyde$height,decreasing = TRUE),]
Klyde


#Subset efter drone model
Klyde_nr <- Klyde[order(Klyde$nr_birds,decreasing = TRUE),]
Klyde_nr

# For Phantom
Klyde_phan <- Klyde[Klyde$id == "Phantom", ]
Klyde_phan

# For Mavic
Klyde_mavic <- Klyde[Klyde$id == "Mavic", ]
Klyde_mavic

#Subset efter drone model både flyvninger og nr_bird
# For Phantom
Klyde_phan <- Klyde[Klyde$id == "Phantom", ]
Klyde_phan_nr <- Klyde_nr[Klyde_nr$id == "Phantom", ]
Klyde_phan
Klyde_phan_nr

# For Mavic
Klyde_mavic <- Klyde[Klyde$id == "Mavic", ]
Klyde_mavic_nr <- Klyde_nr[Klyde_nr$id == "Mavic", ]
Klyde_mavic
Klyde_mavic_nr

```

First we find the number of unique flyover heigths with unique(),
then we find the percentage of flights which are at that flyover height and 

```{r}
Klyde_phan_uni.vec <- unique(Klyde_phan$height)
Klyde_phan_perc_vec <- rep('NA',length(Klyde_phan_uni.vec))
Klyde_phan_perc_vec
for (i in 1:length(unique(Klyde_phan$height))){
   Klyde_phan_perc_vec[i] <- sum((Klyde_phan$height==Klyde_phan_uni.vec[i])/length(Klyde_phan$height))
}
Klyde_phan_cum_vec <- cumsum(Klyde_phan_perc_vec)
Klyde_phan_cum_vec
```

# For Mavic

First we find the number of unique flyover heigths with unique(),
then we find the percentage of flights which are at that flyover height and 

```{r}
Klyde_mavic_uni.vec <- unique(Klyde_mavic$height)
Klyde_mavic_perc_vec <- rep('NA',length(Klyde_mavic_uni.vec))
Klyde_mavic_perc_vec
for (i in 1:length(unique(Klyde_mavic$height))){
   Klyde_mavic_perc_vec[i] <- sum((Klyde_mavic$height==Klyde_mavic_uni.vec[i])/length(Klyde_mavic$height))
}
Klyde_mavic_cum_vec <- cumsum(Klyde_mavic_perc_vec)
Klyde_mavic_cum_vec
```

Lav dataframes

```{r}
phan_Klyde <- data.frame(Klyde_phan_uni.vec,Klyde_phan_cum_vec,id="Phantom")
names(phan_Klyde) <- c("hoejde","percent","id")
ingen_forstyr <- cbind.data.frame(c(100),0,"Phantom")

names(ingen_forstyr) <- c("hoejde","percent","id")

phan_Klyde <- rbind.data.frame(ingen_forstyr,phan_Klyde)
phan_Klyde


mavic_Klyde <- data.frame(Klyde_mavic_uni.vec,Klyde_mavic_cum_vec,id="Mavic")
names(mavic_Klyde) <- c("hoejde","percent","id")
ingen_forstyr <- cbind.data.frame(c(100),0,"Mavic")
names(ingen_forstyr) <- c("hoejde","percent","id")

mavic_Klyde <- rbind.data.frame(ingen_forstyr,mavic_Klyde)
mavic_Klyde

# combine dataframes

Klyde_dat <- rbind.data.frame(phan_Klyde,mavic_Klyde)
Klyde_dat

```

Lav dataframes for nr fugle

```{r}
Klyde_phan_nr

# combine dataframes

Klyde_nr_dat <- rbind.data.frame(Klyde_phan_nr,Klyde_mavic_nr)
Klyde_nr_dat

```


We then use ggplot to visualize each drone by itself

```{r}
p <- ggplot(data = Klyde_dat, aes(x = percent, y = hoejde, group = id,
                               color = id))
p + geom_point() +
  geom_smooth(method = "loess", se = FALSE,  fullrange = TRUE, span = 0.7) + scale_fill_manual(values=c("firebrick1","deepskyblue1"),aesthetics = "colour") + ylim(0, 100) + xlim(0,1.01) +
  ggtitle("Escape distance Avocet") + theme(plot.title = element_text(hjust = 0.5)) + 
  xlab("Percent disturbed") + ylab("Flying altitude")


```

We then use ggplot to visualize each drone by itself (nr fugle)

```{r}
p <- ggplot(data = Klyde_nr_dat, aes(x = nr_birds, y = height, group = id,
                              color = id))
p + geom_point() +
  geom_smooth(method = "gam", se = FALSE,  fullrange = TRUE, span = 0.5) + scale_fill_manual(values=c("deepskyblue1","firebrick1"),aesthetics = "colour") + xlim(0,1000) + ylim(0, 100) +
  ggtitle("Escape distance Avocet") + theme(plot.title = element_text(hjust = 0.5)) + 
  xlab("Flock size disturbed") + ylab("Flying altitude")


```

