
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## For Ryle
Load data as escape distance for the two used UAV models


```{r}

directory <- "F:/Vadehavet/Frames_geo"

Ryle <- file.path(directory,"/Responsafstand_Ryle.csv")
Ryle
Ryle <- read.csv(file=Ryle, header= TRUE)
str(Ryle)

Ryle <- Ryle[order(Ryle$height,decreasing = TRUE),]
Ryle


#Subset efter drone model
Ryle_nr <- Ryle[order(Ryle$nr_birds,decreasing = TRUE),]
Ryle_nr

# For Phantom
Ryle_phan <- Ryle[Ryle$id == "Phantom", ]
Ryle_phan

# For Mavic
Ryle_mavic <- Ryle[Ryle$id == "Mavic", ]
Ryle_mavic

#Subset efter drone model både flyvninger og nr_bird
# For Phantom
Ryle_phan <- Ryle[Ryle$id == "Phantom", ]
Ryle_phan_nr <- Ryle_nr[Ryle_nr$id == "Phantom", ]
Ryle_phan
Ryle_phan_nr

# For Mavic
Ryle_mavic <- Ryle[Ryle$id == "Mavic", ]
Ryle_mavic_nr <- Ryle_nr[Ryle_nr$id == "Mavic", ]
Ryle_mavic
Ryle_mavic_nr

```

First we find the number of unique flyover heigths with unique(),
then we find the percentage of flights which are at that flyover height and 

```{r}
Ryle_phan_uni.vec <- unique(Ryle_phan$height)
Ryle_phan_perc_vec <- rep('NA',length(Ryle_phan_uni.vec))
Ryle_phan_perc_vec
for (i in 1:length(unique(Ryle_phan$height))){
   Ryle_phan_perc_vec[i] <- sum((Ryle_phan$height==Ryle_phan_uni.vec[i])/length(Ryle_phan$height))
}
Ryle_phan_cum_vec <- cumsum(Ryle_phan_perc_vec)
Ryle_phan_cum_vec
```

# For Mavic

First we find the number of unique flyover heigths with unique(),
then we find the percentage of flights which are at that flyover height and 

```{r}
Ryle_mavic_uni.vec <- unique(Ryle_mavic$height)
Ryle_mavic_perc_vec <- rep('NA',length(Ryle_mavic_uni.vec))
Ryle_mavic_perc_vec
for (i in 1:length(unique(Ryle_mavic$height))){
   Ryle_mavic_perc_vec[i] <- sum((Ryle_mavic$height==Ryle_mavic_uni.vec[i])/length(Ryle_mavic$height))
}
Ryle_mavic_cum_vec <- cumsum(Ryle_mavic_perc_vec)
Ryle_mavic_cum_vec
```

Lav dataframes

```{r}
phan_Ryle <- data.frame(Ryle_phan_uni.vec,Ryle_phan_cum_vec,id="Phantom")
names(phan_Ryle) <- c("hoejde","percent","id")
ingen_forstyr <- cbind.data.frame(c(100),0,"Phantom")

names(ingen_forstyr) <- c("hoejde","percent","id")

phan_Ryle <- rbind.data.frame(ingen_forstyr,phan_Ryle)
phan_Ryle


mavic_Ryle <- data.frame(Ryle_mavic_uni.vec,Ryle_mavic_cum_vec,id="Mavic")
names(mavic_Ryle) <- c("hoejde","percent","id")
ingen_forstyr <- cbind.data.frame(c(100),0,"Mavic")
names(ingen_forstyr) <- c("hoejde","percent","id")

mavic_Ryle <- rbind.data.frame(ingen_forstyr,mavic_Ryle)
mavic_Ryle

# combine dataframes

Ryle_dat <- rbind.data.frame(phan_Ryle,mavic_Ryle)
Ryle_dat

```

Lav dataframes for nr fugle

```{r}
Ryle_phan_nr

# combine dataframes

Ryle_nr_dat <- rbind.data.frame(Ryle_phan_nr,Ryle_mavic_nr)
Ryle_nr_dat

```


We then use ggplot to visualize each drone by itself

```{r}
p <- ggplot(data = Ryle_dat, aes(x = percent, y = hoejde, group = id,
                               color = id))
p + geom_point() +
  geom_smooth(method = "loess", se = FALSE,  fullrange = TRUE, span = 0.5) + ylim(0, 100) + xlim(0,1.01) +
  ggtitle("Escape distance Dunlin") + theme(plot.title = element_text(hjust = 0.5)) + 
  xlab("Percent disturbed") + ylab("Flying altitude")


```

We then use ggplot to visualize each drone by itself (nr fugle)

```{r}
p <- ggplot(data = Ryle_nr_dat, aes(x = nr_birds, y = height, group = id,
                               color = id))
p + geom_point() +
  geom_smooth(method = "gam", se = FALSE,  fullrange = TRUE, span = 0.5) + xlim(0,1000) + ylim(0, 100) +
  ggtitle("Escape distance Dunlin") + theme(plot.title = element_text(hjust = 0.5)) + 
  xlab("Flock size disturbed") + ylab("Flying altitude")


```

