
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## For Stormmåge
Load data as escape distance for the two used UAV models


```{r}

directory <- "F:/Vadehavet/Frames_geo"

Stormmåge <- file.path(directory,"/Responsafstand_Stormmåge.csv")
Stormmåge
Stormmåge <- read.csv(file=Stormmåge, header= TRUE)
str(Stormmåge)

Stormmåge <- Stormmåge[order(Stormmåge$height,decreasing = TRUE),]
Stormmåge


#Subset efter drone model
Stormmåge_nr <- Stormmåge[order(Stormmåge$nr_birds,decreasing = TRUE),]
Stormmåge_nr

# For Phantom
Stormmåge_phan <- Stormmåge[Stormmåge$id == "Phantom", ]
Stormmåge_phan

# For Mavic
Stormmåge_mavic <- Stormmåge[Stormmåge$id == "Mavic", ]
Stormmåge_mavic

#Subset efter drone model både flyvninger og nr_bird
# For Phantom
Stormmåge_phan <- Stormmåge[Stormmåge$id == "Phantom", ]
Stormmåge_phan_nr <- Stormmåge_nr[Stormmåge_nr$id == "Phantom", ]
Stormmåge_phan
Stormmåge_phan_nr

# For Mavic
Stormmåge_mavic <- Stormmåge[Stormmåge$id == "Mavic", ]
Stormmåge_mavic_nr <- Stormmåge_nr[Stormmåge_nr$id == "Mavic", ]
Stormmåge_mavic
Stormmåge_mavic_nr

```

First we find the number of unique flyover heigths with unique(),
then we find the percentage of flights which are at that flyover height and 

```{r}
Stormmåge_phan_uni.vec <- unique(Stormmåge_phan$height)
Stormmåge_phan_perc_vec <- rep('NA',length(Stormmåge_phan_uni.vec))
Stormmåge_phan_perc_vec
for (i in 1:length(unique(Stormmåge_phan$height))){
   Stormmåge_phan_perc_vec[i] <- sum((Stormmåge_phan$height==Stormmåge_phan_uni.vec[i])/length(Stormmåge_phan$height))
}
Stormmåge_phan_cum_vec <- cumsum(Stormmåge_phan_perc_vec)
Stormmåge_phan_cum_vec
```

# For Mavic

First we find the number of unique flyover heigths with unique(),
then we find the percentage of flights which are at that flyover height and 

```{r}
Stormmåge_mavic_uni.vec <- unique(Stormmåge_mavic$height)
Stormmåge_mavic_perc_vec <- rep('NA',length(Stormmåge_mavic_uni.vec))
Stormmåge_mavic_perc_vec
for (i in 1:length(unique(Stormmåge_mavic$height))){
   Stormmåge_mavic_perc_vec[i] <- sum((Stormmåge_mavic$height==Stormmåge_mavic_uni.vec[i])/length(Stormmåge_mavic$height))
}
Stormmåge_mavic_cum_vec <- cumsum(Stormmåge_mavic_perc_vec)
Stormmåge_mavic_cum_vec
```

Lav dataframes

```{r}
phan_Stormmåge <- data.frame(Stormmåge_phan_uni.vec,Stormmåge_phan_cum_vec,id="Phantom")
names(phan_Stormmåge) <- c("hoejde","percent","id")
ingen_forstyr <- cbind.data.frame(c(100),0,"Phantom")

names(ingen_forstyr) <- c("hoejde","percent","id")

phan_Stormmåge <- rbind.data.frame(ingen_forstyr,phan_Stormmåge)
phan_Stormmåge


mavic_Stormmåge <- data.frame(Stormmåge_mavic_uni.vec,Stormmåge_mavic_cum_vec,id="Mavic")
names(mavic_Stormmåge) <- c("hoejde","percent","id")
ingen_forstyr <- cbind.data.frame(c(100),0,"Mavic")
names(ingen_forstyr) <- c("hoejde","percent","id")

mavic_Stormmåge <- rbind.data.frame(ingen_forstyr,mavic_Stormmåge)
mavic_Stormmåge

# combine dataframes

Stormmåge_dat <- rbind.data.frame(phan_Stormmåge)
Stormmåge_dat

```

Lav dataframes for nr fugle

```{r}
Stormmåge_phan_nr

# combine dataframes

Stormmåge_nr_dat <- rbind.data.frame(Stormmåge_phan_nr)
Stormmåge_nr_dat

```


We then use ggplot to visualize each drone by itself

```{r}
p <- ggplot(data = Stormmåge_dat, aes(x = percent, y = hoejde, group = id,
                               color = id))
p + geom_point() +
  geom_smooth(method = "loess", se = FALSE,  fullrange = TRUE, span = 0.4) + scale_fill_manual(values=c("firebrick1","deepskyblue1"),aesthetics = "colour") + ylim(0, 100) + xlim(-0.01,1.01) +
  ggtitle("Escape distance Common gull") + theme(plot.title = element_text(hjust = 0.5)) + 
  xlab("Percent disturbed") + ylab("Flying altitude")


```

We then use ggplot to visualize each drone by itself (nr fugle)

```{r}
p <- ggplot(data = Stormmåge_nr_dat, aes(x = nr_birds, y = height, group = id,
                              color = id))
p + geom_point() +
  geom_smooth(method = "gam", se = FALSE,  fullrange = TRUE, span = 0.5) + scale_fill_manual(values=c("firebrick1"),aesthetics = "colour") + xlim(0,1000) + ylim(0, 100) +
  ggtitle("Escape distance Common gull") + theme(plot.title = element_text(hjust = 0.5)) + 
  xlab("Flock size disturbed") + ylab("Flying altitude")


```

