
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## For Storspove
Load data as escape distance for the two used UAV models


```{r}

directory <- "F:/Vadehavet/Frames_geo"

Storspove <- file.path(directory,"/Responsafstand_Storspove.csv")
Storspove
Storspove <- read.csv(file=Storspove, header= TRUE)
str(Storspove)

Storspove <- Storspove[order(Storspove$height,decreasing = TRUE),]
Storspove


#Subset efter drone model
Storspove_nr <- Storspove[order(Storspove$nr_birds,decreasing = TRUE),]
Storspove_nr

# For Phantom
Storspove_phan <- Storspove[Storspove$id == "Phantom", ]
Storspove_phan

# For Mavic
Storspove_mavic <- Storspove[Storspove$id == "Mavic", ]
Storspove_mavic

#Subset efter drone model både flyvninger og nr_bird
# For Phantom
Storspove_phan <- Storspove[Storspove$id == "Phantom", ]
Storspove_phan_nr <- Storspove_nr[Storspove_nr$id == "Phantom", ]
Storspove_phan
Storspove_phan_nr

# For Mavic
Storspove_mavic <- Storspove[Storspove$id == "Mavic", ]
Storspove_mavic_nr <- Storspove_nr[Storspove_nr$id == "Mavic", ]
Storspove_mavic
Storspove_mavic_nr

```

First we find the number of unique flyover heigths with unique(),
then we find the percentage of flights which are at that flyover height and 

```{r}
Storspove_phan_uni.vec <- unique(Storspove_phan$height)
Storspove_phan_perc_vec <- rep('NA',length(Storspove_phan_uni.vec))
Storspove_phan_perc_vec
for (i in 1:length(unique(Storspove_phan$height))){
   Storspove_phan_perc_vec[i] <- sum((Storspove_phan$height==Storspove_phan_uni.vec[i])/length(Storspove_phan$height))
}
Storspove_phan_cum_vec <- cumsum(Storspove_phan_perc_vec)
Storspove_phan_cum_vec
```

# For Mavic

First we find the number of unique flyover heigths with unique(),
then we find the percentage of flights which are at that flyover height and 

```{r}
Storspove_mavic_uni.vec <- unique(Storspove_mavic$height)
Storspove_mavic_perc_vec <- rep('NA',length(Storspove_mavic_uni.vec))
Storspove_mavic_perc_vec
for (i in 1:length(unique(Storspove_mavic$height))){
   Storspove_mavic_perc_vec[i] <- sum((Storspove_mavic$height==Storspove_mavic_uni.vec[i])/length(Storspove_mavic$height))
}
Storspove_mavic_cum_vec <- cumsum(Storspove_mavic_perc_vec)
Storspove_mavic_cum_vec
```

Lav dataframes

```{r}
phan_Storspove <- data.frame(Storspove_phan_uni.vec,Storspove_phan_cum_vec,id="Phantom")
names(phan_Storspove) <- c("hoejde","percent","id")
ingen_forstyr <- cbind.data.frame(c(100),0,"Phantom")

names(ingen_forstyr) <- c("hoejde","percent","id")

phan_Storspove <- rbind.data.frame(ingen_forstyr,phan_Storspove)
phan_Storspove


mavic_Storspove <- data.frame(Storspove_mavic_uni.vec,Storspove_mavic_cum_vec,id="Mavic")
names(mavic_Storspove) <- c("hoejde","percent","id")
ingen_forstyr <- cbind.data.frame(c(100),0,"Mavic")
names(ingen_forstyr) <- c("hoejde","percent","id")

mavic_Storspove <- rbind.data.frame(ingen_forstyr,mavic_Storspove)
mavic_Storspove

# combine dataframes

Storspove_dat <- rbind.data.frame(phan_Storspove,mavic_Storspove)
Storspove_dat

```

Lav dataframes for nr fugle

```{r}
Storspove_phan_nr

# combine dataframes

Storspove_nr_dat <- rbind.data.frame(Storspove_phan_nr,Storspove_mavic_nr)
Storspove_nr_dat

```


We then use ggplot to visualize each drone by itself

```{r}
p <- ggplot(data = Storspove_dat, aes(x = percent, y = hoejde, group = id,
                               color = id))
p + geom_point() +
  geom_smooth(method = "loess", se = FALSE,  fullrange = TRUE, span = 0.7) + scale_fill_manual(values=c("firebrick1","deepskyblue1"),aesthetics = "colour") + ylim(0, 100) + xlim(0,1.01) +
  ggtitle("Escape distance Curlew") + theme(plot.title = element_text(hjust = 0.5)) + 
  xlab("Percent disturbed") + ylab("Flying altitude")


```

We then use ggplot to visualize each drone by itself (nr fugle)

```{r}
p <- ggplot(data = Storspove_nr_dat, aes(x = nr_birds, y = height, group = id,
                              color = id))
p + geom_point() +
  geom_smooth(method = "gam", se = FALSE,  fullrange = TRUE, span = 0.5) + scale_fill_manual(values=c("deepskyblue1","firebrick1"),aesthetics = "colour") + xlim(0,1000) + ylim(0, 100) +
  ggtitle("Escape distance Curlew") + theme(plot.title = element_text(hjust = 0.5)) + 
  xlab("Flock size disturbed") + ylab("Flying altitude")


```

