
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## For Strandskade
Load data as escape distance for the two used UAV models


```{r}

directory <- "F:/Vadehavet/Frames_geo"

Strandskade <- file.path(directory,"/Responsafstand_Strandskade.csv")
Strandskade
Strandskade <- read.csv(file=Strandskade, header= TRUE)
str(Strandskade)

Strandskade <- Strandskade[order(Strandskade$height,decreasing = TRUE),]
Strandskade


#Subset efter drone model
Strandskade_nr <- Strandskade[order(Strandskade$nr_birds,decreasing = TRUE),]
Strandskade_nr

# For Phantom
Strandskade_phan <- Strandskade[Strandskade$id == "Phantom", ]
Strandskade_phan

# For Mavic
Strandskade_mavic <- Strandskade[Strandskade$id == "Mavic", ]
Strandskade_mavic

#Subset efter drone model både flyvninger og nr_bird
# For Phantom
Strandskade_phan <- Strandskade[Strandskade$id == "Phantom", ]
Strandskade_phan_nr <- Strandskade_nr[Strandskade_nr$id == "Phantom", ]
Strandskade_phan
Strandskade_phan_nr

# For Mavic
Strandskade_mavic <- Strandskade[Strandskade$id == "Mavic", ]
Strandskade_mavic_nr <- Strandskade_nr[Strandskade_nr$id == "Mavic", ]
Strandskade_mavic
Strandskade_mavic_nr

```

First we find the number of unique flyover heigths with unique(),
then we find the percentage of flights which are at that flyover height and 

```{r}
Strandskade_phan_uni.vec <- unique(Strandskade_phan$height)
Strandskade_phan_perc_vec <- rep('NA',length(Strandskade_phan_uni.vec))
Strandskade_phan_perc_vec
for (i in 1:length(unique(Strandskade_phan$height))){
   Strandskade_phan_perc_vec[i] <- sum((Strandskade_phan$height==Strandskade_phan_uni.vec[i])/length(Strandskade_phan$height))
}
Strandskade_phan_cum_vec <- cumsum(Strandskade_phan_perc_vec)
Strandskade_phan_cum_vec
```

# For Mavic

First we find the number of unique flyover heigths with unique(),
then we find the percentage of flights which are at that flyover height and 

```{r}
Strandskade_mavic_uni.vec <- unique(Strandskade_mavic$height)
Strandskade_mavic_perc_vec <- rep('NA',length(Strandskade_mavic_uni.vec))
Strandskade_mavic_perc_vec
for (i in 1:length(unique(Strandskade_mavic$height))){
   Strandskade_mavic_perc_vec[i] <- sum((Strandskade_mavic$height==Strandskade_mavic_uni.vec[i])/length(Strandskade_mavic$height))
}
Strandskade_mavic_cum_vec <- cumsum(Strandskade_mavic_perc_vec)
Strandskade_mavic_cum_vec
```

Lav dataframes

```{r}
phan_Strandskade <- data.frame(Strandskade_phan_uni.vec,Strandskade_phan_cum_vec,id="Phantom")
names(phan_Strandskade) <- c("hoejde","percent","id")
ingen_forstyr <- cbind.data.frame(c(100),0,"Phantom")

names(ingen_forstyr) <- c("hoejde","percent","id")

phan_Strandskade <- rbind.data.frame(ingen_forstyr,phan_Strandskade)
phan_Strandskade


mavic_Strandskade <- data.frame(Strandskade_mavic_uni.vec,Strandskade_mavic_cum_vec,id="Mavic")
names(mavic_Strandskade) <- c("hoejde","percent","id")
ingen_forstyr <- cbind.data.frame(c(100),0,"Mavic")
names(ingen_forstyr) <- c("hoejde","percent","id")

mavic_Strandskade <- rbind.data.frame(ingen_forstyr,mavic_Strandskade)
mavic_Strandskade

# combine dataframes

Strandskade_dat <- rbind.data.frame(mavic_Strandskade)
Strandskade_dat

```

Lav dataframes for nr fugle

```{r}
Strandskade_phan_nr

# combine dataframes

Strandskade_nr_dat <- rbind.data.frame(Strandskade_mavic_nr)
Strandskade_nr_dat

```


We then use ggplot to visualize each drone by itself

```{r}
p <- ggplot(data = Strandskade_dat, aes(x = percent, y = hoejde, group = id,
                               color = id))
p + geom_point() +
  geom_smooth(method = "loess", se = FALSE,  fullrange = TRUE, span = 0.7) + scale_fill_manual(values=c("firebrick1","deepskyblue1"),aesthetics = "colour") + ylim(0, 100) + xlim(0,1.01) +
  ggtitle("Escape distance Golden plover") + theme(plot.title = element_text(hjust = 0.5)) + 
  xlab("Percent disturbed") + ylab("Flying altitude")


```

We then use ggplot to visualize each drone by itself (nr fugle)

```{r}
p <- ggplot(data = Strandskade_nr_dat, aes(x = nr_birds, y = height, group = id,
                              color = id))
p + geom_point() +
  geom_smooth(method = "gam", se = FALSE,  fullrange = TRUE, span = 0.5) + scale_fill_manual(values=c("firebrick1"),aesthetics = "colour") + xlim(0,1000) + ylim(0, 100) +
  ggtitle("Escape distance Golden plover") + theme(plot.title = element_text(hjust = 0.5)) + 
  xlab("Flock size disturbed") + ylab("Flying altitude")


```

