---
title: "Untitled"
author: "Jonas Gehrlein"
date: "8 dec 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

Data as escape distance for the two used UAV models

```{r}
phantom <- c(50,60,41,43,43,42,47,51,52,50)
phantom <- as.integer(sort(phantom, decreasing = TRUE))
```

First we find the number of unique flyover heigths with unique(),
then we find the percentage of flights which are at that flyover height and 

```{r}
phan_uni.vec <- unique(phantom)
phan_perc_vec <- rep('NA',length(phan_uni.vec))

for (i in 1:length(unique(phantom))){
   phan_perc_vec[i] <- sum((phantom==phan_uni.vec[i])/length(phantom))
}
phan_cum_vec <- cumsum(phan_perc_vec)

```


```{r}
mavic <- c(30,20,41,33,23,12,27,41,42,30)
mavic <- as.integer(sort(mavic, decreasing = TRUE))
```

First we find the number of unique flyover heigths with unique(),
then we find the percentage of flights which are at that flyover height and 

```{r}
mavic_uni.vec <- unique(mavic)
mavic_perc_vec <- rep('NA',length(mavic_uni.vec))
for (i in 1:length(unique(mavic))){
   mavic_perc_vec[i] <- sum((mavic==mavic_uni.vec[i])/length(mavic))
}

mavic_perc_vec <- as.numeric(mavic_perc_vec)
mavic_cum_vec <- cumsum(mavic_perc_vec)
mavic_perc_vec

```

Lav dataframes

```{r}
phan1 <- data.frame(phan_uni.vec,phan_cum_vec,id="Phantom")
names(phan1) <- c("hoejde","percent","id")
ingen_forstyr <- cbind.data.frame(c(100),0,"Phantom")
names(ingen_forstyr) <- c("hoejde","percent","id")

phan1 <- rbind.data.frame(ingen_forstyr,phan1)
phan1


mavic1 <- data.frame(mavic_uni.vec,mavic_cum_vec,id="Mavic")
names(mavic1) <- c("hoejde","percent","id")
ingen_forstyr <- cbind.data.frame(c(100),0,"Mavic")
names(ingen_forstyr) <- c("hoejde","percent","id")

mavic1 <- rbind.data.frame(ingen_forstyr,mavic1)
mavic1

# combine dataframes

ex_dat_1 <- rbind.data.frame(phan1,mavic1)
ex_dat_1

```


We then use ggplot to visualize each drone by itself

```{r}
p <- ggplot(data = ex_dat_1, aes(x = percent, y = hoejde, group = id,
                               color = id))
p + geom_point() +
  geom_smooth(method = "loess", se = FALSE,  fullrange = TRUE, span = 0.3) + ylim(0, 100) + xlim(0,1) +
  ggtitle("Escape distance Shelduck") + theme(plot.title = element_text(hjust = 0.5))
 + xlab("Percent disturbed") + ylab("Flying altitude")


```

